---
title: "Bing machine"
date: "January 18, 2019"
output:
  html_document:
    fig_caption: yes
    theme: united
    toc: yes
    toc_depth: 3
    toc_float: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(lme4)
library(readr)
library(tidyverse)
library(sjPlot)
library(ggthemes)
library(gridExtra)
library(ggpubr)
library(corrr)
library(reshape2)
library(trimr)

source("Roger_functions/diagnostic_fcns.r")
source("Roger_functions/glmm_stability.r")
source("Roger_functions/boot_glmm.r")
```

```{r loading data, include = FALSE}
bingchild<-read.csv("bingdataR.csv", header=T)
```

```{r data preparation, include=FALSE}
bingchild$z.trialno<-as.vector(scale(bingchild$trialno))
bingchild$z.age=as.vector(scale(bingchild$age))
bingchild$id=as.factor(bingchild$id)

bingchild$agecat=relevel(bingchild$agecat, ref="three")
bingchild$condition=relevel(bingchild$condition, ref="causal")


#coding dummy variables before centering the slopes
bingchild$sex.m<-as.numeric(bingchild$sex==levels(bingchild$sex)[2])
bingchild$condition.arbitrary<-as.numeric(bingchild$condition==levels(bingchild$condition)[2]) ##CJV: condition as categorical variable
bingchild$agecat.four<-as.numeric(bingchild$agecat==levels(bingchild$agecat)[3])
bingchild$agecat.five<-as.numeric(bingchild$agecat==levels(bingchild$agecat)[2])
bingchild$agecat.six<-as.numeric(bingchild$agecat==levels(bingchild$agecat)[4]) #is this correct?# CJV: yes

#centering the slopes
bingchild$sex.m.c<-bingchild$sex.m -mean(bingchild$sex.m)
bingchild$agecat.four.c=bingchild$agecat.four-mean(bingchild$agecat.four)
bingchild$agecat.five.c=bingchild$agecat.five-mean(bingchild$agecat.five)
bingchild$agecat.six.c=bingchild$agecat.four-mean(bingchild$agecat.four)
```



***

```{r eval=FALSE, echo=FALSE}
xx.fe.re=fe.re.tab(fe.model="correct ~ agecat*condition + z.trialno + sex  ",
                   re="(1|id)+ (1|boxtype)",
                   data=data.frame(bingchild))
xx.fe.re$summary
```

###GLMM  

```{r include=FALSE}
contr=glmerControl(optimizer="bobyqa", optCtrl=list(maxfun=10000000))
```

####Full model
```{r}
glmm01_full=glmer(correct ~ agecat*condition + z.trialno + sex + 
                    (1|id) + (1|boxtype) + (0+z.trialno|id),data=bingchild,
                    family=binomial, control=contr) 
```

####Null model	 
```{r echo=FALSE}
glmm01_null=glmer(correct ~ 1+
                    (1|id) + (1|boxtype) + (0+z.trialno|id),data=bingchild,
                    family=binomial, control=contr) 
```

  + Full-null model comparison  
```{r echo=FALSE}	 
round(anova(glmm01_null, glmm01_full, test="Chisq"),3)
```

#####Model output
  + Coefficients
```{r echo=FALSE}
round(summary(glmm01_full)$coefficients, 3)
```


  + Individual predictors: likelihood ratio tests  
Drop1: P values for the individual effects were based on likelihood ratio tests comparing the full with respective reduced models (Barr et al., 2013; R function drop1 with argument 'test' set to "Chisq"). 

```{r echo=FALSE}
xdrop1=drop1(glmm01_full, test="Chisq",control=contr)
round(xdrop1,3)
```

***

###Wilcoxon signed rank tests

```{r include=FALSE}
#install.packages("exactRankTests")
library(exactRankTests)

better.wilcox=function(var1){
  test.data=data.frame(var1)
  test.data=subset( test.data, var1 !=0.5)
  N=nrow(test.data)
  w.res=wilcox.exact (test.data$var1, paired=F, exact=T, mu=0.5, alternative = c("two.sided"))
  wT=w.res$statistic
  wT=max(c(wT, N*(N+1)/2- wT))
return(data.frame(T.plus=wT, N=N, P=w.res$p.value) )
}

better.wilcox2=function(var1, var2){
  test.data=data.frame(var1, var2)
  test.data=subset( test.data, var1 != var2)
  N=nrow(test.data)
  w.res=wilcox.exact (test.data$var1, test.data$var2, paired=T, exact=T, alternative = c("two.sided"))
  wT=w.res$statistic
  wT=max(c(wT, N*(N+1)/2- wT))
return(data.frame(T.plus=wT, N=N, P=w.res$p.value) )
}
```

```{r data aggregation, include=FALSE}

bingchild_individual <- bingchild %>%
  filter(!is.na(correct)) %>%
  group_by(agecat, condition, id) %>% 
  summarize(bing_correct = mean(correct)) %>% 
  add_count(bing_correct)

bingchild_individual_causal <- bingchild %>%
  filter(!is.na(correct)) %>%
  filter(condition=="causal") %>%
  group_by(agecat,id) %>% 
  summarize(bing_correct = mean(correct)) %>% 
  add_count(bing_correct)

bingchild_individual_arbitrary <- bingchild %>%
  filter(!is.na(correct)) %>%
  filter(condition=="arbitrary") %>%
  group_by(agecat,id) %>% 
  summarize(bing_correct = mean(correct)) %>% 
  add_count(bing_correct)


```


#####Causal condition  
```{r echo=FALSE}
wt<-better.wilcox( bingchild_individual_causal[bingchild_individual_causal$agecat=="three",]$bing_correct) 

```
* 3-y-olds:  Median = `r round(median(bingchild_individual_causal[bingchild_individual_causal$agecat=="three",]$bing_correct), 2)`, T<sup>+</sup>=`r wt$T.plus`, N=`r wt$N`, *p*=`r round(wt$P,3)`

```{r echo=FALSE}
wt<-better.wilcox( bingchild_individual_causal[bingchild_individual_causal$agecat=="four",]$bing_correct) 

```
* 4-y-olds:  Median = `r round(median(bingchild_individual_causal[bingchild_individual_causal$agecat=="four",]$bing_correct), 2)`, T<sup>+</sup>=`r wt$T.plus`, N=`r wt$N`, *p*=`r round(wt$P,3)`

```{r echo=FALSE}
wt<-better.wilcox( bingchild_individual_causal[bingchild_individual_causal$agecat=="five",]$bing_correct) 

```
* 5-y-olds:  Median = `r round(median(bingchild_individual_causal[bingchild_individual_causal$agecat=="five",]$bing_correct), 2)`, T<sup>+</sup>=`r wt$T.plus`, N=`r wt$N`, *p*=`r round(wt$P,3)`

```{r echo=FALSE}
wt<-better.wilcox( bingchild_individual_causal[bingchild_individual_causal$agecat=="six",]$bing_correct) 

```
* 6-y-olds:  Median = `r round(median(bingchild_individual_causal[bingchild_individual_causal$agecat=="six",]$bing_correct), 2)`, T<sup>+</sup>=`r wt$T.plus`, N=`r wt$N`, *p*=`r round(wt$P,3)`



#####Arbitrary condition  
```{r echo=FALSE}
wt<-better.wilcox( bingchild_individual_arbitrary[bingchild_individual_arbitrary$agecat=="three",]$bing_correct) 

```
* 3-y-olds:  Median = `r round(median(bingchild_individual_arbitrary[bingchild_individual_arbitrary$agecat=="three",]$bing_correct), 2)`, T<sup>+</sup>=`r wt$T.plus`, N=`r wt$N`, *p*=`r round(wt$P,3)`

```{r echo=FALSE}
wt<-better.wilcox( bingchild_individual_arbitrary[bingchild_individual_arbitrary$agecat=="four",]$bing_correct) 

```
* 4-y-olds:  Median = `r round(median(bingchild_individual_arbitrary[bingchild_individual_arbitrary$agecat=="four",]$bing_correct), 2)`, T<sup>+</sup>=`r wt$T.plus`, N=`r wt$N`, *p*=`r round(wt$P,3)`

```{r echo=FALSE}
wt<-better.wilcox( bingchild_individual_arbitrary[bingchild_individual_arbitrary$agecat=="five",]$bing_correct) 

```
* 5-y-olds:  Median = `r round(median(bingchild_individual_arbitrary[bingchild_individual_arbitrary$agecat=="five",]$bing_correct), 2)`, T<sup>+</sup>=`r wt$T.plus`, N=`r wt$N`, *p*=`r round(wt$P,3)`

```{r echo=FALSE}
wt<-better.wilcox( bingchild_individual_arbitrary[bingchild_individual_arbitrary$agecat=="six",]$bing_correct) 

```
* 6-y-olds:  Median = `r round(median(bingchild_individual_arbitrary[bingchild_individual_arbitrary$agecat=="six",]$bing_correct), 2)`, T<sup>+</sup>=`r wt$T.plus`, N=`r wt$N`, *p*=`r round(wt$P,3)`

###Mann-Whitney U-Test  

####Causal vs arbitrary condition
```{r echo=FALSE}
mt<-wilcox.exact(bingchild_individual[bingchild_individual$agecat=="three",]$bing_correct~bingchild_individual[bingchild_individual$agecat=="three",]$condition,exact=T)
#The test statistic is 'U', despite labelled 'W'but it is not always the smaller of the two U-values to get the smaller (its a convention to indicate this) use:
u_mt<-min(c(mt$statistic, prod(table(bingchild_individual[bingchild_individual$agecat=="three",]$condition))-mt$statistic))
#to get the sample sizes use:
n1_mt<-table(bingchild_individual[bingchild_individual$agecat=="three",]$condition)[1]
n2_mt<-table(bingchild_individual[bingchild_individual$agecat=="three",]$condition)[2]
```
* 3-y-olds: Difference between causal and arbitrary condition: U=`r u_mt`, N<sub>causal</sub>=`r n1_mt`, N<sub>arbitrary</sub>=`r n2_mt`, *p*=`r round(mt$p.value, 3)`

```{r echo=FALSE}
mt<-wilcox.exact(bingchild_individual[bingchild_individual$agecat=="four",]$bing_correct~bingchild_individual[bingchild_individual$agecat=="four",]$condition,exact=T)
#The test statistic is 'U', despite labelled 'W'but it is not always the smaller of the two U-values to get the smaller (its a convention to indicate this) use:
u_mt<-min(c(mt$statistic, prod(table(bingchild_individual[bingchild_individual$agecat=="four",]$condition))-mt$statistic))
#to get the sample sizes use:
n1_mt<-table(bingchild_individual[bingchild_individual$agecat=="four",]$condition)[1]
n2_mt<-table(bingchild_individual[bingchild_individual$agecat=="four",]$condition)[2]
```
* 4-y-olds: Difference between causal and arbitrary condition: U=`r u_mt`, N<sub>causal</sub>=`r n1_mt`, N<sub>arbitrary</sub>=`r n2_mt`, *p*=`r round(mt$p.value, 3)`

```{r echo=FALSE}
mt<-wilcox.exact(bingchild_individual[bingchild_individual$agecat=="five",]$bing_correct~bingchild_individual[bingchild_individual$agecat=="five",]$condition,exact=T)
#The test statistic is 'U', despite labelled 'W'but it is not always the smaller of the two U-values to get the smaller (its a convention to indicate this) use:
u_mt<-min(c(mt$statistic, prod(table(bingchild_individual[bingchild_individual$agecat=="five",]$condition))-mt$statistic))
#to get the sample sizes use:
n1_mt<-table(bingchild_individual[bingchild_individual$agecat=="five",]$condition)[1]
n2_mt<-table(bingchild_individual[bingchild_individual$agecat=="five",]$condition)[2]
```
* 5-y-olds: Difference between causal and arbitrary condition: U=`r u_mt`, N<sub>causal</sub>=`r n1_mt`, N<sub>arbitrary</sub>=`r n2_mt`, *p*=`r round(mt$p.value, 3)`

```{r echo=FALSE}
mt<-wilcox.exact(bingchild_individual[bingchild_individual$agecat=="six",]$bing_correct~bingchild_individual[bingchild_individual$agecat=="six",]$condition,exact=T)
#The test statistic is 'U', despite labelled 'W'but it is not always the smaller of the two U-values to get the smaller (its a convention to indicate this) use:
u_mt<-min(c(mt$statistic, prod(table(bingchild_individual[bingchild_individual$agecat=="six",]$condition))-mt$statistic))
#to get the sample sizes use:
n1_mt<-table(bingchild_individual[bingchild_individual$agecat=="six",]$condition)[1]
n2_mt<-table(bingchild_individual[bingchild_individual$agecat=="six",]$condition)[2]
```
* 6-y-olds: Difference between causal and arbitrary condition: U=`r u_mt`, N<sub>causal</sub>=`r n1_mt`, N<sub>arbitrary</sub>=`r n2_mt`, *p*=`r round(mt$p.value, 3)`







